\newpage
\section{Conclusion}

	\qquad This comprehensive report delves into the realm of stochastic programming, exploring its practical applications within industrial manufacturing and disaster response planning. It lays the foundation by elucidating the core principles of stochastic programming, elucidating the intricacies of stochastic programs and the methodologies employed to address such complexities. Delving deeper, it meticulously elucidates the formulation of a 2-stage stochastic linear programming problem with recourse, vividly illustrating the intricate relationship between the stages and underscoring the imperative nature of optimizing decisions amidst uncertain parameters.

	\qquad Moving forward, the report presents the implementation and comparison of two distinct algorithms—Primal Dual and Successive Shortest Path. These algorithms are employed to solve the minimum cost max flow problem posited in Li Wang's research. Subsequently, an extensive runtime analysis is conducted, rigorously scrutinizing the efficiency and comparative effectiveness of Algorithm 1 as proposed in the aforementioned research.

	\qquad This extensive exploration and experimentation with 2-stage stochastic programming problems have cultivated a profound comprehension of the subject matter. As a result, it lays a solid foundation for further research and application, paving the way for enhanced problem-solving approaches and strategies in complex decision-making scenarios in our path in the future.
